%File: main.tex
%Based on formatting-instructions.tex, distributed as part of the aaai submission information.
\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\frenchspacing

\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Link Prediction in FanFiction Networks)
/Author (Alexander Hayes)}
\setcounter{secnumdepth}{0}

\begin{document}
% The file aaai.sty is the style file for AAAI Press
% proceedings, working notes, and technical reports.
%
\title{Link Prediction in FanFiction Networks}
\author{Alexander L. Hayes\\
The University of Texas at Dallas\\
alexander.hayes@utdallas.edu\\
}

\maketitle
\begin{abstract}
\begin{quote}
The author performs link prediction on metadata scraped from FanFiction.Net (the world's largest repository of user-submitted fanfiction), applying statistical relational learning to predict authorship. Code and documentation for the experiments are available on GitHub.\footnote{\texttt{https://github.com/batflyer/FanFiction-\\Collaborative-Filtering}}
\end{quote}
\end{abstract}

\section{Introduction}
A ``fanfic'' is a creative work where an author adapts or extends an existing work of fiction.

\subsection{Background}

FanFiction has been observed through a variety of academic lenses; such as psychology, sociology, and computer science. Though many have taken interest in the subject, a common viewpoint is that fanfiction is poorly understood within academic literature, or that previous attempts to analyze fanfiction communities have been performed in disruptive manners \cite{larsen2011fandom}. \cite{barnes2015fanfiction} noted that the subject at the time of writing had almost entirely been understood from a qualitative standpoint.

\subsection{Related Work}

Within the last few years has there been an increase in large-scale computational analyses. \cite{milli2016beyond} compared fanfiction with the source (canon) text that stories originated from, sentiment analysis on the reviews, and predicted how readers would respond to characters in a chapter. \cite{yin2017no} published an anonymized set of metadata, and presented evidence that the majority of users were English-speaking students based on the time of year FanFiction.Net users were most active.

\section{Experiments}

The authors employ a state-of-the-art statistical relational learning system: \textit{BoostSRL} in order to both model the communities as entities, relations, and attributes. All authors and stories on FanFiction.Net may be identified by a unique integer, these identifiers (and their respective meta-data) lend themselves naturally to a relational representation. The meta-data about each story includes attributes such as the number of words, number of chapters, main characters, genres, and rating. Stories may be introduced with a summary in fewer than 384 characters, but these are not included here. Stories may be divided into chapters, and chapters may be reviewed by the author or other community members.

\section{Appendix}

\subsection{Scraping FanFiction.Net}

The terms of service for FanFiction.Net state the limitations of launching automated bots in Section 4, Paragraph E of their terms of service\footnote{https://www.fanfiction.net/tos/}, paraphrased here:

\begin{itemize}
    \item ``You agree not to use or launch any automated system... that accesses the Website in a manner that sends more request messages... than a human can reasonably produce in the same period....''
    \item ``FanFiction.Net grants the operators of public search engines permission to use spiders... solely to the extent necessary for creating publicly available searchable indices... but not caches or archives....''
    \item ``You agree not to collect or harvest any personally identifiable information... for any commercial solicitation purposes.''
\end{itemize}

Scraping FanFiction.Net may be accomplished via the \texttt{scraper/} directory of this repository. The core documentation pertaining to each script and their respective functions are contained therein, this discussion pertains to the high-level idea of what they accomplish.

All users and stories on FanFiction.Net may be identified via a unique id-number. These id-numbers may be used to directly access one or the other, for example: user \textit{124}'s profile may be found by sending a request to https://www.fanfiction.net/u/124. In a similar manner, story \textit{124} would be at https://www.fanfiction.net/s/124. Reviews for a story follow the pattern \texttt{/r/125/0/1/}, where the first integer corresponds the story-id, the second integer to a certain chapter (or 0 for all reviews), and the third is a page number (a maximum of 15 reviews are displayed on each page, so any overflow will be on subsequent pages).

\bibliographystyle{aaai}
\bibliography{link-prediction-fanfiction}

\end{document}
